---
title: "Rendering HTML outputs"
output: html_notebook
---

# Rendering the HTML

This notebook renders HTML outputs from the 01 notebook through *parameterisation*.

Make sure that you open Index.Rmd and 'knit' that file to create an index.html file in the _site folder first.

## Import the data

First we import the data in order to generate a list of authorities that we can use to specify the parameters and name the files.

```{r import data}
fileloc = "https://docs.google.com/spreadsheets/d/e/2PACX-1vTRm8tw8O_QO_o4bk4Y_3sUlX0N5ukNrCeHj08RyShS3cAEmKTZdvB8g48zDHbl8l_dmDtjOUUrB12L/pub?gid=814230511&single=true&output=csv"
data = read.csv(fileloc, stringsAsFactors = F)
#just get one column - it's now a vector
la <- data$la_name
```

We remove two of those which combine figures where authorities changed.

```{r generate sample}
#this reduces to just a few while testing
#we exclude the last two which are combined authorities
la <- la[1:155]
#la <- la[1:10]
#la

```


## Render a markdown file for each LA

The code below takes the Rmd file named and renders a .md file for each area (even though the file itself specifies html_document as its output). 

The files are placed in a subfolder called 'site'.

This is because the next notebook then renders the entire folder as a website, so the HTML in those .md files becomes active.

```{r generate md files}
#store the location of the paramsfile to use below
paramsfile <- "01latemplate.Rmd"
#loop through all regions 
for (r in la) {
  print(r)
  rmarkdown::render(paramsfile, params = list(la = r), output_file = paste(sep="",'site/',stringr::str_replace_all(r," ","-"),'.md'),
    envir = parent.frame())
}
#we remove the space in the name as this appears to create a file missing the navbar
#str_remove_all(r," ")
#more at https://bookdown.org/yihui/rmarkdown-cookbook/rmarkdown-render.html

```