---
title: "Render and clean"
output: md_notebook
---

# Rendering the website and cleaning the HTML files

* In notebook 1 a template was created that could be used to generate text descriptions and tables for each authority
* In notebook 2 dozens of different markdown files were generated from that template

This notebook details the next step: combining those pages into a website, and generating an index page.

## Store a list of markdown files

First, we need to store a list of all the files that are going to be used. These are in a folder called 'site'.

We then loop through those file names and, for those which end in '.md', we use those names to generate some code and store it in a YAML file within the same 'site' folder.

```{r get file names and generate yaml}
#code adapted from https://github.com/BBC-Data-Unit/police_misconduct/blob/main/rfiles/03renderAndClean.Rmd
#get the names of all the html files
filenames <- list.files("site")
#store the string we want to start out yaml file with
yamlstring <- 'name: "la"
navbar:
  title: "Schools see language needs rise post lockdown"
  left:
    - text: "Local authorities"
      menu:'
#create an empty vector to store all the strings we're about to create
strvec <- c()
#loop through the filenames 
for (i in filenames){
  if(substring(i,nchar(i)-2,nchar(i)) == ".md" ){
    #replace spaces with dashes, and replace the file extension with .html
    htmlversion <- gsub(" ","-",gsub(".md",".html",i))
    #get the name by removing the file extension. 
    textversion <- gsub(".md","",i)
    #create a string for the YAML file by inserting those
    fullstring <- paste0('
      - text: "',textversion,'"
        href: ',htmlversion)
    strvec <- c(strvec,fullstring) #add to the collection of strings 
  }
}
#add the initial string
strvec <- c(yamlstring, strvec)
#create a yaml file with that string of text in it
write(strvec, file = "site/_site.yml")
```

## Render the files

Finally, we use the `render_site` function to specify the folder containing all the files for the site. The YAML file will be used to generate a menu, among other things.

The resulting HTML files are moved to another subfolder, called '_site'.

```{r render site}
#now render the site
rmarkdown::render_site("site")
```

We also want to render the index file. 

## Clean the HTML outputs

The pages have some HTML which needs to be removed because it is being rendered as paragraph text: `<p>&lt;!DOCTYPE html&gt;</p>`.

```{r list html files}
#get the names of all the html files
htmlfiles <- list.files("site/_site")
htmlfiles[4]
#read in the first one
testfile <- readr::read_lines(paste0("site/_site/",htmlfiles[4]))
#create an empty list
tfvec <- c()
#loop through all the lines
for(i in testfile){
  #check if the line matches the string
  tfmatch <- i == "<p>&lt;!DOCTYPE html&gt;</p>"
  #store the True/False value in a vector
  tfvec <- c(tfvec,tfmatch)
}

#find the index of the line with that text
doctypeline <- which(tfvec)
print(doctypeline)
#show the  line
#testfile[174]
testfile[doctypeline]
#replace it
testfile[doctypeline] <- ""
testfile[doctypeline]
#save it as a HTML file to check
write(x = testfile, file=paste0("site/_site/","testfile.html"))
#remove the variable
rm(testfile)
```


Once tested, we embed that process in a loop which tests if the file is one of the pages and then removes the offending line if so.

```{r clean all files}
#create a list to catch matches
matchlist <- c()
#loop through the list of filenames
for (i in htmlfiles){
  print(i)
  #extract the last 5 chars
  filetype <- substring(i,nchar(i)-4,nchar(i))
  #check if they end in .html
  ey <- filetype == ".html"
  print(filetype)
  #this should be TRUE or FALSE
  print(ey)
  #if it's a html file
  if(ey){
    #read in that file
    thisfile <- readr::read_lines(paste0("site/_site/",i))
    #show line
    print(thisfile[174])
    #if it has that text
    if (thisfile[174] == "<p>&lt;!DOCTYPE html&gt;</p>"){
      print("OH 174!")
      #replace specified string
      thisfile[174] <- ""
      write(x = thisfile, file=paste0("site/_site/",i))
    }
    #grab the same line we identified in the code chunk above
    else if(thisfile[doctypeline] == "<p>&lt;!DOCTYPE html&gt;</p>"){
      stringtoprint <- paste("OH",doctypeline,"!")
      print(stringtoprint)
      #replace specified string
      thisfile[doctypeline] <- ""
      write(x = thisfile, file=paste0("site/_site/",i))
    }
    else {
      print("NOPE")
      #add filename to list
      matchlist <- c(matchlist,i)
    }
  }
  else {
    print("NOT THIS ONE")
  }
}
```


### Clean up the index page menus

We also need to clean the dropdown menu in the index page: by default this lists all the forces but is too long to fit on one screen and cannot be scrolled. 

So we need to split it into multiple menus instead.


```{r clean index menu}
#read it in
indexfile <- readr::read_lines("site/_site/index.html")
#line 256 should be the title of the dropdown, 'Local authorities'
indexfile[256]
#change it
indexfile[256] <- "Local authorities A-B"
indexfile[256]
#line 322 should be the beginning of the first C authority, Calderdale
indexfile[321:323]
#add HTML which closes the first part of the list and begins a second list with a dropdown button
#code taken from https://github.com/sduiopc/test1/blob/8938ef49cf45eb5cb67ab73974c8bdbf33aee4c5/index.html
#which is the version where I did this manually
indexfile[321] <- '</ul></li></ul><ul class="nav navbar-nav navbar-right"></ul><ul class="nav navbar-nav"><li class="dropdown"><a href="#" class="dropdown-toggle" data-toggle="dropdown" role="button" aria-expanded="false">C-E<span class="caret"></span></a><ul class="dropdown-menu" role="menu"><li>'
indexfile[321:323]
#replace 'Cen' as this is a dead link
indexfile[327:329] <- ""
#now for the first authority after Essex
indexfile[393:395]
#split there too
indexfile[393] <- '</ul></li></ul><ul class="nav navbar-nav navbar-right"></ul><ul class="nav navbar-nav"><li class="dropdown"><a href="#" class="dropdown-toggle" data-toggle="dropdown" role="button" aria-expanded="false">G-K<span class="caret"></span></a><ul class="dropdown-menu" role="menu"><li>'
#split on Lambeth
indexfile[462:464]
indexfile[462] <- '</ul></li></ul><ul class="nav navbar-nav navbar-right"></ul><ul class="nav navbar-nav"><li class="dropdown"><a href="#" class="dropdown-toggle" data-toggle="dropdown" role="button" aria-expanded="false">L-M<span class="caret"></span></a><ul class="dropdown-menu" role="menu"><li>'
#split on Newcastle
indexfile[504:506]
indexfile[504] <- '</ul></li></ul><ul class="nav navbar-nav navbar-right"></ul><ul class="nav navbar-nav"><li class="dropdown"><a href="#" class="dropdown-toggle" data-toggle="dropdown" role="button" aria-expanded="false">N-P<span class="caret"></span></a><ul class="dropdown-menu" role="menu"><li>'
#split on Reading
indexfile[561:563]
indexfile[561] <- '</ul></li></ul><ul class="nav navbar-nav navbar-right"></ul><ul class="nav navbar-nav"><li class="dropdown"><a href="#" class="dropdown-toggle" data-toggle="dropdown" role="button" aria-expanded="false">R<span class="caret"></span></a><ul class="dropdown-menu" role="menu"><li>'
#split on Salford
indexfile[582:584]
indexfile[582] <- '</ul></li></ul><ul class="nav navbar-nav navbar-right"></ul><ul class="nav navbar-nav"><li class="dropdown"><a href="#" class="dropdown-toggle" data-toggle="dropdown" role="button" aria-expanded="false">S<span class="caret"></span></a><ul class="dropdown-menu" role="menu"><li>'
#split on Tameside
indexfile[651:653]
indexfile[651] <- '</ul></li></ul><ul class="nav navbar-nav navbar-right"></ul><ul class="nav navbar-nav"><li class="dropdown"><a href="#" class="dropdown-toggle" data-toggle="dropdown" role="button" aria-expanded="false">T-Z<span class="caret"></span></a><ul class="dropdown-menu" role="menu"><li>'
indexfile[663:665] <- ""
#save file
write(x = indexfile, file=paste0("site/_site/","index.html"))
```

## Clean the navigation in other pages

We need to ensure this navbar is the same in all pages.

We also need to remove the duplicate `<html>` tag which otherwise prevents the navbar working. This and other duplicate lines of code run from lines 745-889.


```{r remove nav in area files}
#store the line numbers for the starting points so we only have to change them here
menutitleline <- 254
htmlline <- 743

#create a list to catch matches
matchlist <- c()
#loop through the list of filenames
for (i in htmlfiles){
  print(i)
  #extract the last 5 chars
  filetype <- substring(i,nchar(i)-4,nchar(i))
  #check if they end in .html
  ey <- filetype == ".html"
  print(filetype)
  #this should be TRUE or FALSE
  print(ey)
  #we don't want to change the index.html file so set to false if it's that file
  if(i == 'index.html'){
    print("NOT THIS ONE")
    ey <- FALSE
  }
  #if it's a html file (apart from index.html)
  if(ey){
    #read in that file
    thisfile <- readr::read_lines(paste0("site/_site/",i))
    #line 254 should be the title of the dropdown, 'Local authorities'
    print(thisfile[menutitleline])
    #if it has that text
    if (thisfile[menutitleline] == '    Local authorities'){
      print(paste("OH ",menutitleline,"!"))
      #replace specified string
      #change it
      thisfile[menutitleline] <- "Local authorities A-B"
      #line 322 should be the beginning of the first C authority, Calderdale
      #print(thisfile[menutitleline+65])
      thisfile[menutitleline+65] <- '</ul></li></ul><ul class="nav navbar-nav navbar-right"></ul><ul class="nav navbar-nav"><li class="dropdown"><a href="#" class="dropdown-toggle" data-toggle="dropdown" role="button" aria-expanded="false">C-E<span class="caret"></span></a><ul class="dropdown-menu" role="menu"><li>'
      #replace 'Cen' as this is a dead link
      thisfile[(menutitleline+71):(menutitleline+73)] <- ""
      #now for the first authority after Essex
      thisfile[menutitleline+137] <- '</ul></li></ul><ul class="nav navbar-nav navbar-right"></ul><ul class="nav navbar-nav"><li class="dropdown"><a href="#" class="dropdown-toggle" data-toggle="dropdown" role="button" aria-expanded="false">G-K<span class="caret"></span></a><ul class="dropdown-menu" role="menu"><li>'
      #split on Lambeth
      thisfile[menutitleline+206] <- '</ul></li></ul><ul class="nav navbar-nav navbar-right"></ul><ul class="nav navbar-nav"><li class="dropdown"><a href="#" class="dropdown-toggle" data-toggle="dropdown" role="button" aria-expanded="false">L-M<span class="caret"></span></a><ul class="dropdown-menu" role="menu"><li>'
      #split on Newcastle
      thisfile[menutitleline+248] <- '</ul></li></ul><ul class="nav navbar-nav navbar-right"></ul><ul class="nav navbar-nav"><li class="dropdown"><a href="#" class="dropdown-toggle" data-toggle="dropdown" role="button" aria-expanded="false">N-P<span class="caret"></span></a><ul class="dropdown-menu" role="menu"><li>'
      #split on Reading
      thisfile[menutitleline+305] <- '</ul></li></ul><ul class="nav navbar-nav navbar-right"></ul><ul class="nav navbar-nav"><li class="dropdown"><a href="#" class="dropdown-toggle" data-toggle="dropdown" role="button" aria-expanded="false">R<span class="caret"></span></a><ul class="dropdown-menu" role="menu"><li>'
      #split on Salford
      thisfile[menutitleline+326] <- '</ul></li></ul><ul class="nav navbar-nav navbar-right"></ul><ul class="nav navbar-nav"><li class="dropdown"><a href="#" class="dropdown-toggle" data-toggle="dropdown" role="button" aria-expanded="false">S<span class="caret"></span></a><ul class="dropdown-menu" role="menu"><li>'
      #split on Tameside
      #print(thisfile[(menutitleline+395):(menutitleline+397)])
      thisfile[menutitleline+395] <- '</ul></li></ul><ul class="nav navbar-nav navbar-right"></ul><ul class="nav navbar-nav"><li class="dropdown"><a href="#" class="dropdown-toggle" data-toggle="dropdown" role="button" aria-expanded="false">T-Z<span class="caret"></span></a><ul class="dropdown-menu" role="menu"><li>'
      #print(thisfile[(menutitleline+407):(menutitleline+409)])
      thisfile[(menutitleline+407):(menutitleline+409)] <- ""
      
      #now to clean up the extra <html> and <head> tags
      print(thisfile[htmlline])
      #this should be the start of body
      print(thisfile[htmlline+144])
      #replace from <html> to </head>
      thisfile[htmlline:(htmlline+14)] <- ""
      
      write(x = thisfile, file=paste0("site/_site/",i))
    }
  }
  else {
    print("NOT THIS ONE")
  }
}
```



```{r remove index file variable}
#remove the variable
rm(indexfile)
```

