---
title: "Wales analysis"
output: html_notebook
---

# Analysing data on SEN in Wales

The data has been downloaded manually from StatsWales's [Reports of additional learning or special educational needs by local authority and type of need](https://statswales.gov.wales/Catalogue/Education-and-Skills/Schools-and-Teachers/Schools-Census/Pupil-Level-Annual-School-Census/Special-Educational-Needs/reportsofspecialeducationalneeds-by-localauthority-typeofneed) in 5 CSV files.

## Import the data, and clean

We now import those.

```{r import data}
wales22 <- read.csv("walesdata/export.csv", skip = 6)
wales21 <- read.csv("walesdata/export(1).csv", skip = 6)
wales20 <- read.csv("walesdata/export(2).csv", skip = 6)
wales19 <- read.csv("walesdata/export(3).csv", skip = 6)
wales18 <- read.csv("walesdata/export(4).csv", skip = 6)
```

Add the year.

```{r add year}
wales22$year <- "21/22"
wales21$year <- "20/21"
wales20$year <- "19/20"
wales19$year <- "18/19"
wales18$year <- "17/18"
```

And combine into a single data frame.

```{r combine data}
wales18to22 <- rbind(wales18, wales19, wales20, wales21, wales22)
```

The first column name is missing so we add that.

```{r rename column 1}
colnames(wales18to22)[1] <- "local_authority"
colnames(wales18to22)
```

```{r export wales18to22}
write.csv(wales18to22, "wales18to22.csv")
```


## Import pupil totals

We need to check if there's been a drop in pupil numbers


```{r import pup data}
wales22 <- read.csv("walesdata_pupils/export.csv", skip = 6)
wales21 <- read.csv("walesdata_pupils/export(1).csv", skip = 6)
wales20 <- read.csv("walesdata_pupils/export(2).csv", skip = 6)
wales19 <- read.csv("walesdata_pupils/export(3).csv", skip = 6)
wales18 <- read.csv("walesdata_pupils/export(4).csv", skip = 6)
```

Add the year.

```{r add year pup}
wales22$year <- "21/22"
wales21$year <- "20/21"
wales20$year <- "19/20"
wales19$year <- "18/19"
wales18$year <- "17/18"
```

And combine into a single data frame.

```{r combine pup data}
wales18to22_pupils <- rbind(wales18, wales19, wales20, wales21, wales22)
```

The first column name is missing so we add that.

```{r rename column 1 pup}
colnames(wales18to22_pupils)[1] <- "local_authority"
colnames(wales18to22_pupils)
```

```{r export wales18to22 pup}
write.csv(wales18to22_pupils, "wales18to22_pup.csv")
```

